\documentclass[letterpaper,10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\input{glyphtounicode}
% Use Times New Roman font
\usepackage{newtxtext,newtxmath}
\usepackage[hidelinks]{hyperref}

% Page style and spacing
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlist{nosep,leftmargin=*}

% Section formatting: 12pt headings
\titleformat{\section}{\fontsize{13pt}{15pt}\selectfont\scshape}{}{0em}{}[\color{black}\titlerule]
\titlespacing*{\section}{0pt}{1pt}{1pt}

% Ensure machine-readable PDF
\pdfgentounicode=1

% List commands
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt,label={},itemsep=2pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=\textbullet,leftmargin=0.2in,itemsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}
% Subheading: Title left, date right, then description left with GPA/date bolded right
\newcommand{\resumeSubheading}[4]{\item {\textbf{#1}}\hfill{\textbf{#2}}\\
  {#3}\hfill{\textbf{#4}}}
\newcommand{\resumeItem}[1]{\item #1}

% Document start
\begin{document}
\vspace*{-0.45in}

%----------HEADING----------
\begin{center}
  {\fontsize{15pt}{16pt}\selectfont\bfseries Jane Doe}\\
  \vspace{2pt}
  {\normalsize 555-123-4567 \textbar\ \href{mailto:jane.doe@university.edu}{jane.doe@university.edu} \textbar\
  \href{https://www.linkedin.com/in/jane-doe/}{linkedin.com/in/jane-doe} \textbar\
  \href{https://github.com/janedoe}{github.com/janedoe}}
\end{center}

%-----------EDUCATION-----------
\section{\textbf{Education}}
\resumeSubHeadingListStart
  \resumeSubheading{University of Florida $|$ Gainesville}{Aug. 2023 -- May 2027}{Bachelor of Science in Computer Science, Minors: Statistics, Electrical Engineering}{GPA: 4.0}
  \item Certificates in AI Fundamentals and Applications and Data Analytics
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{\textbf{Experience}}
\resumeSubHeadingListStart
  \item {\textbf{AI Solutions Engineer Intern}} \hfill {\textbf{Jan. 2026 -- Present}}\\
    \textbf{Fortune 500 Appliance Company $|$ Louisville, KY}
  \resumeItemListStart
    \resumeItem{Built an \textbf{Agentic} QA Review application whose Director agent orchestrates specialized sub-agents across codebase and webapp reviews to generate \textbf{bug reports, test plans, and repo specs}.}
    \resumeItem{Created a PR QA gate with \textbf{GitHub Agentic Workflows} in \textbf{GitHub Actions} that reviews changed Python files and all files in a \textbf{1-hop blast radius}, posts a bug report and test plan, and blocks merges on \textbf{Critical/High} findings.}
  \resumeItemListEnd
  \item {\textbf{AI Scholars Researcher}} \hfill {\textbf{Aug. 2025 -- Present}}\\
    \textbf{School of Construction Management $|$ University of Florida}
  \resumeItemListStart
    \resumeItem{Published research in the \textbf{UF Journal of Undergraduate Research} on using \textbf{machine learning} to predict whether safety warning signals are audible or masked in 4-second construction-noise clips.}
    \resumeItem{Built an \textbf{end-to-end audio ML pipeline} that preprocessed construction-noise clips, synthesized warning signals, generated labeled mixtures, derived acoustic features and mel-spectrograms, and trained models to detect masked safety alarms.}
  \resumeItemListEnd
  \item {\textbf{System Administrator Intern}} \hfill {\textbf{May 2025 -- Present}}\\
    \textbf{IFAS $|$ University of Florida}
  \resumeItemListStart
    \resumeItem{Managed technology needs for \textbf{25+ faculty}, providing technical support and leading system maintenance, imaging, and deployment to ensure seamless technology integration and reliability.}
    \resumeItem{Created a dedicated laptop \textbf{OU} in \textbf{Active Directory} and linked a custom \textbf{GPO} to automate biweekly maintenance, running Dell Command Update and Windows security updates every other Sunday.}
  \resumeItemListEnd
   \item {\textbf{AI Engineer Intern}} \hfill {\textbf{Jun. 2025 -- Aug. 2025}}\\
    \textbf{Government Contractor $|$ NASA Johnson Space Center (JSC)}
  \resumeItemListStart
    \resumeItem{Reduced manual anomaly detection time by \textbf{12 hours} by assisting in the development of an \textbf{autoencoder} using \textbf{PyTorch} to detect anomalies for ISS exercise machine sensor faults, processing over \textbf{11,000} data points per exercise set in \textbf{large-scale time-series data}.}
    \resumeItem{Engineered a comprehensive dashboard using \textbf{Dash, Plotly, and SciPy}, implemented a \textbf{CI/CD pipeline} with \textbf{PyTest} and GitLab runners to ensure code quality and deployed an \textbf{end-to-end data pipeline} with \textbf{Dagster}.}
  \resumeItemListEnd
  \item {\textbf{Undergraduate Research Assistant}} \hfill {\textbf{Oct. 2024 -- May 2025}}\\
    \textbf{School of Construction Management $|$ University of Florida}
  \resumeItemListStart
    \resumeItem{Developed a \textbf{CTGAN synthesizer} using \textbf{SDV} and Python to generate high-fidelity synthetic data, enabling initial \textbf{neural network training} in the absence of real-world data.}
    \resumeItem{Identified and analyzed key \textbf{physiological (5--8)} and \textbf{environmental (12--13)} variables to inform early model development for predicting heat-related illness risk in construction settings.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{\textbf{Projects}}
\resumeSubHeadingListStart
  \item{\textbf{ExperienceCurator AI $|$ Python, FastAPI, PostgreSQL, pgvector, ADK, Docker, React/TypeScript}}\hfill\textbf{Dec. 2025 -- Present}
  \resumeItemListStart
  \resumeItem{Built a ``career memory'' system with \textbf{agent-orchestrated RAG workflows} to ingest docs and codebases, normalize content, generate embeddings, and serve evidence-grounded answers through a FastAPI REST API with pgvector retrieval.}
  \resumeItem{Implemented \textbf{multi-agent} resume tailoring and interview preparation tools, reducing resume customization time by \textbf{30\%} through \textbf{citation-grounded} bullet suggestions and generating concise, sourced answers to user-created interview questions.}
  \resumeItemListEnd
  \item{\textbf{EvoChess $|$ Python, PyTorch, MLflow, Dagster, AWS S3, Docker, Google Cloud Run}}\hfill\textbf{Mar. 2025 -- Apr. 2025}
  \resumeItemListStart
  \resumeItem{Orchestrated an \textbf{automated MLOps pipeline} with Dagster to ETL chess game data from Lichess into AWS S3 for \textbf{CNN model} training with PyTorch, and deployed the final model as a containerized API using Docker and Google Cloud Run.}
  \resumeItem{Trained a Convolutional Neural Network in PyTorch on a filtered dataset of \textbf{9,000,000+ games rated 2000+ elo}, engineering a data processing workflow to predict optimal move sequences from any given board state.}
  \resumeItemListEnd
  \item{\textbf{Data-Driven Resource Optimization $|$ Python, Matplotlib, Scikit-learn}}\hfill\textbf{Jul. 2024 -- Aug. 2024}
  \resumeItemListStart
    \resumeItem{Developed a \textbf{gradient descent} algorithm to minimize Mean Squared Error (MSE) for predicting event resource needs, achieving an \textbf{R\textsuperscript{2} score of 0.958} with Scikit-learn and reducing costs by \textbf{20\%} with an \textbf{85\%} decrease in waste.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS AND ACHIEVEMENTS-----------
\section{\textbf{Skills and Achievements}}
\resumeSubHeadingListStart
  \item{\textbf{ML/AI}: PyTorch, Scikit-learn, LangChain, Google ADK, CrewAI, RAG, CNNs, Autoencoders, Time-Series Analysis}
  \item{\textbf{Production \& MLOps}: FastAPI, Docker, Dagster, MLflow, Github Actions CI/CD, OAuth 2.0, PyTest, Git, Linux}
  \item{\textbf{Cloud \& Data}: Terraform, AWS, GCP, PostgreSQL (pgvector), MongoDB, InfluxDB, Pandas, Plotly, Dash}
  \item{\textbf{Languages}: Python, TypeScript, SQL, C++, R}
  \item{\textbf{Awards}: Intern Scholarship (2025), AI Scholar (2025), University President's Honor Roll (2024--Present)}
\resumeSubHeadingListEnd

\end{document}
